---
title: "HireArt_Exercise"
output:
  html_document: default
  pdf_document: default
---

- Reading xlsx file by installing and using library readxl.
- Set working directory. 
- Use function read_excel to extract data fromxlsx file.
- Showed top 5 rows of data using function head() 

```{r}
#install.packages("readxl")
library(readxl)
setwd('D:/wallpaper')
my_data = read_excel('HireArt - Data Analyst Exercise 10.12.17.xlsx')
head(my_data, n= 5)
```

- Checked count of missing values in a data, using sum() and is.na().
- There are 0 missing values in a data.


```{r}
sum(is.na(my_data))

```

- Extracted month from  Date of Contact using months().
- Create dataframe(df_1) and included all the values of my_data and month.
- Displayed top 5 rows using function head().

```{r}

Month_of_Contact = months(my_data$`Date of Contact`, abbreviate = TRUE)

df_1 = data.frame(my_data$`Account manager`, my_data$`Client Name`,my_data$`Date of Contact`, Month_of_Contact)

head(df_1, n=5)
```


-created frequency table for months.

```{r}
library(plyr)
Count_month = count(df_1$Month_of_Contact)
Count_month
```

- Used ggplot2 libraries.
- Utilized ggplot() visualization function to display bar plot of variable : Month and frequency of Month.
- Here we can conclude that October is a month when clients are contacted in a greatest percentage by team

```{r}
library(ggplot2)
ggplot(Count_month, aes(x = x, y = freq), size = 1)+ geom_bar(stat = "Identity", width = .4, fill = "RED") + scale_x_discrete(limits = month.abb)
```